---
title: "SP500"
author: "Johnson Ekedum"
date: "March 27, 2017"
output: html_document
---


** [Github Directory path] (https://github.com/jdpersona/SP500.git)

```{r setup, include=FALSE}
library(tseries)
```
1.  TODO: Download the data of SP500 '^gspc'.
```{r }
SNPdata <- get.hist.quote('^gspc',quote="Close")

```

2. TODO: Calculate the log returns, which is the subtractration of log(lag(SNPdata)) and 
```{r}

SNPret <- lag(SNPdata) - log(SNPdata)

```
3. TODO: Calculate volatility measure that is to multiply sd(SNPret),sqrt(250), 100
```{r}
SNPvol <- sd(SNPret) * sqrt(250) * 100
```

*  Define getVol function for volatility
```{r}
getVol <- function(d, logrets) {
	var = 0
	lam = 0
	varlist <- c()

	for (r in logrets) {
		lam = lam*(1 - 1/d) + 1
	  var = (1 - 1/lam)*var + (1/lam)*r^2
		varlist <- c(varlist, var)
	}

	sqrt(varlist)
}
```

* Calculate volatility over entire length of series for various three different decay factors: 10 30. 100

4.  TODO: call getVol function with the parameters: 10,SNPret

```{r}
volest <- getVol(10,SNPret)

```
5.  TODO: call getVol function with the parameters: 30,SNPret
```{r}

volest2 <- getVol(30,SNPret)
```
6.  TODO: call getVol function with the parameters: 100,SNPret
```{r}
volest3 <- getVol(100,SNPret)
```
7.  Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
8. TODO: Add connected line segments for volest2 with the parameters: type="l",col="red"
9. TODO: Add connected line segments for volest3 with the parameters: type="l",col="blue"

```{r}
plot(volest,type="l")
lines(volest2, y = NULL, type = "l",col="red")
lines(volest3, y = NULL, type = "l",col="blue")

```
